SDSS-GAIA Calibration Note

### 2022-08-11 ms.tex
Figures are added

>>>>

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220810_airmass_vs_dmag_dr8star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220810_airmass_vs_dmag_dr8quasar.png}
\caption{DR8 : Now we do the test again.  This time, we compare synthesized mag from the observed spectra.  Note the ones above are synthesized mag from the best model spectra. Several percent offset, but not too bad. Stars left, and Quasars right.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=8.9cm]{figures/20220810_airmass_vs_dmag_dr17star.png}
\includegraphics[angle=0,width=8.9cm]{figures/20220810_airmass_vs_dmag_dr17quasar.png}
\caption{DR17 : Now SDSS-III/IV data are being calibrated by Daniel Margala's method.  It has greatly imporved the flux calibration.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_u_dr8stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_g_dr8stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_r_dr8stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_i_dr8stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_z_dr8stars.png}
\caption{DR8 Star: Histogram of synthesized magnitude from spectra vs PSF magnitude.
u-band shows a large offset but it is due to spectral wavelength does not cover entire u-band region.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_u_dr8quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_g_dr8quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_r_dr8quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_i_dr8quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_z_dr8quasars.png}
\caption{DR8 Quasar: Histogram of synthesized magnitude from spectra vs PSF magnitude.
u-band shows a large offset but it is due to spectral wavelength does not cover entire u-band region.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_u_dr17stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_g_dr17stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_r_dr17stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_i_dr17stars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_z_dr17stars.png}
\caption{DR17 Star: Histogram of synthesized magnitude from spectra vs PSF magnitude.
u-band shows a large offset but it is due to spectral wavelength does not cover entire u-band region.}
\end{center}
\end{figure*}

\begin{figure*}%[ht]
\begin{center}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_u_dr17quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_g_dr17quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_r_dr17quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_i_dr17quasars.png}
\includegraphics[angle=0,width=3.5cm]{figures/20220811_dmag_histogram_z_dr17quasars.png}
\caption{DR17 Quasar: Histogram of synthesized magnitude from spectra vs PSF magnitude.
u-band shows a large offset but it is due to spectral wavelength does not cover entire u-band region.}
\end{center}
\end{figure*}
